An Extensible Approach to Verification of Embedded Network Systems*

### 2014-04-22 tech-project/paper.tex
refined some of the previous sections -- wording, etc

\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own. This is ideal in a setting where drivers might encompass a wide spectrum possible applications, where each might require unique, new mathematical developments.% reword this to be less vague.

@@

The paper is organized as follows: First, we open with a brief overview of the Telos mote platform. Next, we present revised specifications of an LED driver component with a formally verified enhancement. This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used. The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code. We conclude with suggestions for tool improvements, as well as a review of some longer term research goals.

@@

The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley. Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory. A cc2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors. The mote also contains three onboard LEDs: One blue, one red, and one green.

@@

Finally, the concept provides two operations. The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}. The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} upon completion that: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}. The \texttt{Status} operation is specified similarly.

@@

In this section we give a short overview of the verification results of \texttt{Toggling\_Realiz}. The first step in proving this particular realization correct is to generate verification conditions (VCs), which, if proven, will establish the correctness of this particular realization\footnote{Note: VCs themselves are typically generated from specific lines of a realization to ensure that the overall content of a realization is consistent with its specification.}.

@@

As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness. In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety. Readers interested however in learning more about how the prover goes about transforming and dispatching similar (and other, more complex) VCs should refer to \cite{smith:2013}.

@@

Shown below is a RESOLVE facility module that implements the client logic of this embedded application.
\begin{verbatim}
Facility LED_Telos_Demo;
    uses Std_Clock_Fac;

@@

end LED_Telos_Demo;
\end{verbatim}
%smaller file sizes
%reusable code
%only have to translate a file once
% be able to say that the code we have is the code that was verified.
% our approach takes less ROM. Its not less efficient, it is differently efficient.
Prior to using the LED component developed in the previous sections, we first must associate our \texttt{LED\_Template} specification with an appropriate realization. This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}). Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.

@@

RESOLVE, however, in its current state is far too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so. In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing. In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization, that matches as closely as possible the conventions and model of translation later detailed in Section \#.

@@

We feel this new keyword is useful for the following reasons:
\begin{itemize}
\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code. The keyword now transparently indicates this.
\item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
\end{itemize}

In the context of embedded systems especially, we feel these developments will allow users to flexibly and transparently specify all low level components of the sort required in most embedded applications (e.g. LED strip drivers). It is our intent that new (native) resolve components are layered on top of these low level drivers to provide a system (not unlike NesC) that deals with verified component graphs of ..

@@

% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE... AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE. BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
\section{Implementation}
Development of the tool presented here can be logically partitioned into three distinct phases: 
\begin{enumerate}
\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
\item Implementing reusable mechanisms for carrying out the C code generation process.
\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
\end{enumerate}
In this section we discuss each of these phases, concluding with a demo illustrating each working in tandem to realize the example presented in section \ref{sec:specifiying}.

>>>>

\item \textbf{Mathematical flexibility} RESOLVE offers a rich, mathematical type system that allows users to either draw from a library of preexisting mathematical units when writing specifications, or simply create their own. This is ideal in a setting where drivers might encompass a wide spectrum possible applications wherein the need for new mathematical developments may arise.% reword this to be less vague.

@@

The paper is organized as follows: First, we open with a brief overview of the Telos mote platform. Next, we present revised specifications of an LED driver component that is accompanied by a small enhancement. This section is concluded with a review of verification results, and a discussion of any relevant theorems and verification conditions (VCs) used. The remainder of the paper is spent detailing the model of C code generated by the tool, giving a quick overview of generation process itself, and detailing a dynamic, stack-based memory allocation tool utilized by the translated code. We conclude with a review of related works and suggestions for future research and tool improvements.

@@

The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley. Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory. A cc2420 radio stack provides broadcast and receiving capabilities, while optional sensing capabilities may be added to the mote in the form of light, humidity, and temperature sensors. The mote also contains three onboard LEDs: One blue, one red, and one green.

@@

Finally, the concept provides two operations. The first, \texttt{Set}, takes as a parameter an instance of an LED strip \texttt{L}, a boolean \texttt{b}, and an integer \texttt{i}. The operation \texttt{requires} that \texttt{i} falls within the length of the strip, and \texttt{ensures} two things upon completion: The length of the outgoing strip \texttt{L} is the same as the incoming strip, \texttt{\#L}, and that the LED in position \texttt{i} of \texttt{L} is set to boolean \texttt{b}. The \texttt{Status} operation is specified similarly.

@@

We now turn to the task of verifying our small toggling enhancement. The first step in doing so is to generate Verification Conditions (VCs) for \texttt{Toggle\_Realiz}, which, if proven, will establish the correctness of this particular implementation of \texttt{Toggling\_Capability}. One thing to note about the VCs themselves is that they are generated from specific lines of a realization, and exist to ensure that the content of the realization is consistent with its specification: This entails checking for things such as array access boundary violations, etc.

@@

As the results summarized in Figure \ref{fig:results} indicate, using RESOLVE's integrated prover, we are able to mechanically and automatically dispatch all VCs for \texttt{Toggling\_Realiz}, thus verifying its correctness. In terms of proof difficulty, given the number of steps and time taken to establish each, we conclude that the VCs generated were of a straightforward variety. Readers interested however in learning more about the steps and specific actions the prover takes in transforming givens and dispatching similar (and more complex) VCs should refer to \cite{smith:2013}.

@@

Shown below is a RESOLVE facility module that implements the client logic of this embedded application.
\begin{verbatim}
Facility LED_Telos_Demo;
    uses Std_Clock_Fac, Std_Boolean_Fac, 
            Std_Integer_Fac;

@@

end LED_Telos_Demo;
\end{verbatim}
%smaller file sizes
%reusable code
%only have to translate a file once
% be able to say that the code we have is the code that was verified.
% our approach takes less ROM. Its not less efficient, it is differently efficient.
Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization. This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}). Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion.

@@

RESOLVE, however, in its current state is too high level of a language to perform these tasks directly -- meaning it lacks the appropriate driver and language support to do so. In an effort to address this, we introduce the notion of \textit{external realizations}, which allow users to write their own realization of a concept in a language of their choosing. In the case of \texttt{LED\_Template}, we chose to provide a hand written \texttt{Std\_Leds\_Realiz} C realization, that matches as closely as possible the conventions and model of translation later detailed in Section \#.

@@

We feel this new keyword is useful for the following reasons:
\begin{itemize}
\item The language no longer must ``hide" the fact that some of the lower level components relied upon are not written in straight-line, native RESOLVE code. The ``externally" keyword now transparently indicates this.
\item Provides flexibility for those users looking to wrap their low-level programs/drivers with formal RESOLVE interface specifications.
\end{itemize}

In the context of embedded systems especially, we feel these developments allow flexibility and transparency in the way users specify low level components of the sort required in most embedded applications (e.g. LED strip drivers). It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually building up to a system (not unlike NesC) that deals exclusively in verified, native RESOLVE components.

@@

% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE... AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE. BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
\section{Implementation}
Development of our C translation tool can be logically partitioned into three distinct pieces: 
\begin{enumerate}
\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
\item Implementing reusable mechanisms for carrying out the C code generation process.
\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
\end{enumerate}
In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.
